---
title: Concept of linear programming
author: Deependra Dhakal
date: \today
classoption: compress
toc: true
output: binb::monash
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, dev.args=list(bg=grey(0.9), pointsize=11))
```

# Intro

## General form

In general linear programming model can be written as:

$$
\text{Max Z} = \sum_{j=1}^{n}{C_jX_i}
\tag{1.0}
$$

Subject to

$$
\begin{align}
\sum_{j=1}^{n}{a_{ij}X_i} &\leq bi ; i = 1,2,3...,m
\tag{1.1}
\end{align}
$$

and

$$
\begin{align}
X_j &\geq 0; j = 1, 2, 3...,n
\tag{1.2}
\end{align}
$$

where,

$$
\begin{align}
Z &= \text{total gross margin} \\
X_j &= \text{the level of the}\ j^{th}\ \text{activity} \\
C_j &= \text{the gross margin of the}\ j^{th}\ \text{activity} \\
a_{ij} &= \text{the quantity of the}\ i^{th}\ \text{resource required to produce a unit of}\ j^{th}\ \text{activity} \\
b_i &= \text{the amount of the}\ i^{th}\ \text{resource available}
\end{align}
$$


### Some enumeration

1. The first item
1. Stuff
1. Nonsense

# Using R

## Slide with R output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with graphics

```{r pressure}
plot(pressure)
```

## Slide with mathematics

Quantile score for observation $y$. For $0<p<1$:

\begin{block}{}
  \[
    S(y_t,q_t(p)) = \left\{
      \begin{array}{rl}
            p(y_t-q_t(p)) & \text{if $y_t \ge q_t(p)$}\\
        (1-p)(q_t(p)-y_t) & \text{if $y_t < q_t(p)$}
      \end{array}\right.
  \]
\end{block}

Average score over all percentiles gives the best distribution forecast:
\[
  QS = \frac{1}{99T}\sum_{p=1}^{99}\sum_{t=1}^T S(q_t(p),y_t)
\]

# RMarkdown Examples

## R Figure

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

\small

```{r pressureCode, eval=FALSE, echo=TRUE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "orange",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```


## R Figure

```{r pressureFig, echo=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "orange",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```

## R Table

A simple `knitr::kable` example:

\small

```{r kableEx, echo=TRUE}
knitr::kable(mtcars[1:4, 1:7],
       caption="(Parts of) the mtcars dataset")
```

## Resources

### For more information:
- See the [RMarkdown repository](https://github.com/rstudio/rmarkdown) for more on RMarkdown
- See the [binb repository](https://github.com/eddelbuettel/binb) for more on binb
- See the [binb vignettes](https://github.com/eddelbuettel/binb/vignettes) for more examples.
