---
title: Mixed integer programming
subtitle: 
author: Deependra Dhakal
date: August, 2019
institute: |
  | \textit{ddhakal.rookie@gmail.com}
  | \url{https://rookie.rbind.io}
output: 
  binb::metropolis:
    includes:
      in_header: beamer_header_template.tex
classoption: "aspectratio=169" # "compressed"
fontsize: 11pt
bibliography: [./bibliographies.bib]
---

```{r,setup, include=FALSE}
library(knitr)
require(tidyverse)
set.seed(453)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, echo = FALSE, 
                  message = FALSE, warning = FALSE,
                  out.width = "45%", cache = TRUE)
options(knitr.table.format = "latex")
options(knitr.kable.NA = "", digits = 2)
options(kableExtra.latex.load_packages = FALSE)
```

# Background

##

- Learn more about integer programming: https://en.wikipedia.org/wiki/Integer_programming
- Learn from a tutorial post on Assigning students to courses on: https://www.r-orms.org/mixed-integer-linear-programming/practicals/problem-course-assignment/
- A discourse on Generalized Assignment Problem is found at (combinatorial optimization): https://en.wikipedia.org/wiki/Generalized_assignment_problem
- Adapt this to fix a problem where we would like to match a group of teachers to a set of classes schedules for different semesters with the following constraints:
  - Each day classess will run for 2 semester
  - Each semester has a capacity to take fixed number of classes in a day
  - Every teacher needs to be assigned to exactly 1 class in each semester. Thus a total of 2 classess each day
  - All teachers have stated individual preferences on a scale from 1(early morning) to 3 (late morning), where 3 is the most favorable time to take class.

##

```{r}
library(ompr)
library(ompr.roi)
require(tidyverse)
# the base package ROI offers plugin extensions to different solvers
# these solvers are then used by ompr
# install.packages("~/Downloads/ROI.plugin.glpk_0.3-0.tar.gz", repos = NULL, type = "source")
require(ROI.plugin.glpk) # needs libglpk-dev library

# n number of teachers
n <- 6

# And m classes with equal capacity (suppose). The capacity can vary among courses though.
m <- 3 # each teacher must take in both class
capacity <- rep.int(2, m) # both semesters have equal capacities of taking daily classess, suppose 3 

# In addition, each teacher has three preferences. 
# To model this we have a function that gives us 3 classes for each teacher. 
# The first component has preference 1, second 2, and third 3:

set.seed(1234)
preference_data <- lapply(seq_len(n), function(x) sample(seq_len(m), 2, replace = FALSE))
preferences <- function(teacher) preference_data[[teacher]]

preferences(2) # preference for class for each teacher. Since there are only two semesters, 
```

##

- For warehouse location problem see this page: https://dirkschumacher.github.io/ompr/articles/problem-warehouse-location.html

- Types of problems solved by ompr and modelling techniques (with other solvers): https://dirkschumacher.github.io/ompr/articles/modelling.html

##

```{r}
# Knapsack problem solving (requires glpk to be installed)
# Learn more about the knapsack problem: https://en.wikipedia.org/wiki/Knapsack_problem
library(dplyr)
library(ROI)
library(ROI.plugin.glpk)
library(ompr)
library(ompr.roi)
max_capacity <- 5
n <- 10
weights <- runif(n, max = max_capacity)
MIPModel() %>%
  add_variable(x[i], i = 1:n, type = "binary") %>%
  set_objective(sum_expr(weights[i] * x[i], i = 1:n), "max") %>%
  add_constraint(sum_expr(weights[i] * x[i], i = 1:n) <= max_capacity) %>%
  solve_model(with_ROI(solver = "glpk")) %>% 
  get_solution(x[i]) %>% 
  filter(value > 0)

```

##

- For sudoku solving: https://www.r-orms.org/mixed-integer-linear-programming/practicals/problem-sudoku/
- After finishing Generalized assignment, knapsack problem and sudoku solving, hop into travelling salesman problem: https://www.r-orms.org/mixed-integer-linear-programming/practicals/problem-tsp/
- For more advanced problems refer to matchingMarkets package (requires lpSolve), this inturn uses libgmp-dev gnu library

# Bibliography

## References
